---
title: "Example: Combined Issues"
author: "Student C"
date: "2025-01-15"
output: html_document
---

## Real-World Scenario

This file combines multiple common issues that instructors encounter.

```{r setup, message=FALSE}
library(tidyverse)
library(here)
```

## Issue 1: Bare file path

```{r}
# Will be fixed to use here::here()
data <- read_csv("student_data.csv")
```

## Issue 2: Failed chunk with bare path

```{r}
# Both the path AND the error will be fixed
# The path gets wrapped, and eval=FALSE is added
results <- read_csv("missing_file.csv")
model <- lm(nonexistent ~ formula, data = results)
```

## Issue 3: Successful analysis

```{r}
# This works and will be preserved
summary_stats <- data.frame(
  mean = mean(1:10),
  sd = sd(1:10)
)
print(summary_stats)
```

## Issue 4: Another path that works but needs fixing

```{r}
# File exists but path needs to be portable
config <- readRDS("config.rds")
```

## Note

The fix_rmd() function handles all these issues in one pass:
- Wraps bare paths with here::here()
- Adds eval=FALSE only to chunks that actually fail
- Preserves working code and student formatting
- Creates backup before any modifications
