---
title: "Example: Failing Code Chunks"
author: "Student B"
date: "2025-01-15"
output: html_document
---

## Introduction

This submission has several chunks that will fail to execute.

## Successful Setup

```{r setup}
x <- 10
y <- 20
z <- x + y
```

## Typo in Function Name

```{r}
# Student made a typo - this will fail
result <- maen(c(1, 2, 3, 4, 5))  # Should be 'mean'
```

## Using Previous Results

```{r}
# This chunk depends on the previous one but will still run
# because fix_rmd() marks the failed chunk as eval=FALSE
total <- x + y
print(total)
```

## Undefined Variable

```{r}
# Student forgot to define this variable
analysis <- undefined_variable * 2
```

## Working Chunk

```{r}
# This will work fine
summary(1:100)
```

## Note

After running fix_rmd() on this file, chunks with errors will have
'eval = FALSE' added to their headers, but working chunks remain unchanged.
The file will knit successfully with the working chunks executed and
error chunks displayed but not run.
